Multi-modality Imagery Database for Plant Phenotyping

### 2015-10-20 datapaper_baseline.tex
figure size

Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
Therefore, it will not be applied to bean imagery as it does not belong to rosette plant.
%In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.

@@

\begin{figure*}
\begin{centering}
\begin{tabular}{c c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
%\begin{tabular}{lllllllll}
(a) &
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
(b)&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_9}\\
(c) &
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\

@@

%Leaf alignment provides the leaf candidates for tracking over time.
Figure~\ref{fig:trackExample} shows the leaf tracking result of one Arabidopsis video in both fluorescence and RGB modalities.
We can see the high quality leaf label propagation results on this video.
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Figure~\ref{fig:trackExample} (b),(e), purple leaf replaces the red leaf at day $6$.
%Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample} (c)).
Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
However, they are still evaluated as well aligned and segmented leaves.

>>>>

Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
Therefore, it will not be applied to bean imagery, as it does not belong to rosette plant.
%In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.

@@

\begin{figure*}
\begin{centering}
\begin{tabular}{c c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
%\begin{tabular}{lllllllll}
(a) &
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
(b)&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_9}\\
(c) &
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.png}&
\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.png}&
\includegraphics[trim= 100 70 120 10,  clip, width=.1\textwidth]{Figures/trackExample/3_9.png}\\

@@

%Leaf alignment provides the leaf candidates for tracking over time.
Figure~\ref{fig:trackExample} shows the leaf tracking result of one Arabidopsis video in both fluorescence and RGB modalities.
We can see the high quality leaf label propagation results on this video.
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Figure~\ref{fig:trackExample} (b),(e), purple leaf replaces the red leaf at day $6$.
%Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample} (c)).
Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t. the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
However, they are still evaluated as well aligned and segmented leaves.

### 2015-10-20 datapaper_conclusion.tex
figure size

It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.

>>>>

% Jeff's comments
It should be obvious that all plants in MSU-PID belong to the same genotype and that no treatments were applied to induce phenotypic differences.  
This is because we have chosen to focus on a fundamental issue with visual phenotyping, i.e. accurate and automated identification and tracking of individual leaves over developmental time scales (days to weeks).  
The inherent challenge is that as leaves emerge and grow they change in size, position and shape and they may overlap or be overlapped by other leaves.  
Yet, as emphasized in the introduction, these factors may be important determinants for defining phenotypic differences between/among groups.  
In addition, development of these methods would invaluable for providing data to refine models of photosynthesis in plants with more complex canopies and in canopy systems.  
%It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
%This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
%The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
%We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.

### 2015-10-20 datapaper_hardware.tex
revision_2
figure size

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
Note that the other modalities were captured only at day time, so that they will not interfere with the circadian cycle of the plant.

@@

\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.
The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.  The color images are JPEG-compressed coming out of the sensor and so have block artefacts.  The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain depth estimates at each pixel~\cite{Hansard2013}.

@@

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$. The distance to the target bean plant is roughly $620~mm$ in this example.  The image planes are plotted at depths proportional to the focal lengths.  The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

>>>>

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
Note that the other modalities were captured only at daytime, so that they will not interfere with the circadian cycle of the plant.

@@

\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.
The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.  The color images are JPEG-compressed coming out of the sensor and so have block artifacts.  The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain depth estimates at each pixel~\cite{Hansard2013}.

@@

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$. The distance to the target bean plant is roughly $620~mm$ in this example. For clarity the image planes are plotted not at actual target depth, where they would overlap, but at depths proportional to their focal lengths. The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and it is further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

### 2015-10-20 datapapr_labeling.tex
figure size

\section{Annotation, Files and Protocol}
\subsection{Data Statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and bean.
The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
In order to make sure that all four modalities are present at the same time, we release the part of images captured only in the day hours, which are $15$ images per day for Arabidopsis and $13$ for bean for all four modalities.

@@

Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.

@@

To quantify the precision of the label propagation, we manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities.
The labels in each modality is propagated on other modalities.
The result of one plant is illustrated in Figure~\ref{fig:LabelAlignment}.
This mapping will introduce errors due to depth-based parallax.
We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual labels and the propagated labels.
In order to compute the inter-annotators variability, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score.
The results are shown in Table~\ref{tab:labelError}.

@@

The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
The availability of multiple modalities allows user to design novel experimental setup.
For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent,Chen2013b}.

@@

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{yin2015}.
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three metrics as follows:
\begin{itemize}
\item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves.
This can attribute to two sources.
The first is miss detections and false alarms.
The second is matched leaves with tip-based errors larger than $\tau$.
When $\tau$ is large enough, this value is equal to the leaf counting error.
\item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
This is used to measure the leaf tip alignment error.
\item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
This is used to measure leaf tracking accuracy.
\end{itemize}

>>>>

\section{Annotation, Files and Protocol}
\subsection{Data Statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and bean.
The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants cannot be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
In order to make sure that all four modalities are present at the same time, we release the part of images captured only in the day hours, which are $15$ images per day for Arabidopsis and $13$ for bean for all four modalities.

@@

Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves; the extra effort of breaking a super pixel into two makes it a less efficient alternative.

@@

To quantify the precision of the label propagation, we manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities.
The label in each modality is propagated on other modalities.
The result of one plant is illustrated in Figure~\ref{fig:LabelAlignment}.
This mapping will introduce errors due to depth-based parallax.
We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual labels and the propagated labels.
In order to compute the inter-annotators variability, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score.
The results are shown in Table~\ref{tab:labelError}.

@@

The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
The availability of multiple modalities allows user to design novel experimental setup.
For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transferring learning with missing modality~\cite{ding2014latent,Chen2013b}.

@@

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{yin2015}.
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three metrics as follows:
\begin{itemize}
\item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves.
This can attribute to two sources.
The first is miss detections and false alarms.
The second is matched leaves with tip-based errors larger than $\tau$.
When $\tau$ is large enough, this value is equal to the leaf counting error.
\item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
This is used to measure the leaf tip alignment error.
\item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
This is used to measure leaf-tracking accuracy.
\end{itemize}
